Last glacial cycle glacier erosion potential in the Alps

### 2021-06-01 articles/erosion/response-referee1.md

## References not in the manuscript:

In addition to the aforementioned changes, the Sternai et al. (2013) reference
was added in the discussion of the vertical distribution of erosion with this
new sentence:

    Over longer timescales, though, the vertical distribution of erosion rates
    also depends on the erosional modification of topography (Sternai et al.,
    2013).

Thank you again for taking the time to read our work and to give constructive
feedback in these troubled times. We hope that you will find our answers
satisfactory, apologize for the delay and will soon be submitting a revised
and, we believe, improved manuscript including the aforementioned suggested
changes.

### 2021-06-01 articles/erosion/alps-erosion.tex
Extend the video supplement paragraph.

\videosupplement{
    Animations made available online show the modelled glacier erosion rates
    (\url{https://vimeo.com/503162771}), and their evolving relationship with
    ice volume (\url{https://vimeo.com/512478926}) and bedrock
    altitude (\url{https://vimeo.com/512479008}).}

>>>>

\videosupplement{
    Animations made available online show the spatio-temporal distribution of
    modelled glacier potential erosion rates
    (\url{https://vimeo.com/503162771}, supplementing
    Fig.~\ref{fig:cumulative}), the evolving relationship between ice volume
    and potential annual erosion volume (\url{https://vimeo.com/512478926},
    supplementing Fig.~\ref{fig:evolution}), and the distribution of potential
    erosion rate against bedrock altitude (\url{https://vimeo.com/512479008},
    supplementing Fig.~\ref{fig:hypsogram}).}
